---
title: "Source code for 'Sportscasters don't get shrinkage'"
output: github_document
---

This repository contains code to generate the slides for a presentation "Sporstcasters don't get shrinkage" to Analyze Boulder on 2016-12-07. 

### Making the slides

The slides are produced from R Markdown (`slides.Rmd`), which requires that you have LaTeX, beamer, and the following R packages installed from CRAN:

```{r, eval = FALSE}
install.packages(c("ggplot2, tidyr, dplyr, rstan, modeest, 
                   viridis, flux, Lahman, bayesplot", "devtools", "knitr"))
```

The basketball data are scraped using an in-development package [`bbr`](https://www.github.com/mbjoseph/bbr), which can be installed directly from GitHub using devtools:

```{r, eval = FALSE}
devtools::install_github("mbjoseph/bbr")
```

Once the dependencies are satisfied, knit the document with:

```{r, eval = FALSE}
knitr::knit("slides.Rmd", "slides.pdf")
```

If this runs successfully, you will see a pdf in the top level directory: `slides.pdf`.

### I don't want to make the slides, I just want to download them!

You can download the pdf here: https://dl.dropboxusercontent.com/u/18637425/ab-shrinkage-slides.pdf
